%-------------------------
% Resume in LaTeX
% Author : Vishwa R
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=black, urlcolor=black, citecolor=black]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Fix the footskip issue
\setlength{\footskip}{4.08003pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}
\newcommand{\hackthon}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Vishwa R} \\ \vspace{1pt}
    \small
    \faEnvelope\hspace{1mm}\href{mailto:vishwa0r1@gmail.com}{vishwa0r1@gmail.com} $|$ 
    \faPhone\hspace{1mm}\href{tel:+917708690518}{+91-7708690518} $|$
    \href{https://linkedin.com/in/r-vishwa}{linkedin.com/in/vishwar} $|$ 
    \href{https://github.com/01Vishwa}{github.com/vishwar} $|$ 
    \faUser\hspace{1mm}\href{https://bento.me/vishwa}{Portfolio} %$|$ 
    %\faIcon{map-marker-alt}\hspace{1mm}Coimbatore, India
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Coimbatore Institute of Technology}{Coimbatore, India}
      {M.Sc Decision and Computing Sciences – CGPA: 7.91/10.0 (8th Sem)}{2021 -- 2026}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Data Science Intern}{June 2024 -- Present}
      {Prediscan Medtech}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented a deep learning regression model using PyTorch to extract clinical biomarkers from retinal fundus images, enabling non-invasive diagnostics.}
        \resumeItem{Engineered a robust data pipeline with augmentation techniques (e.g., flips, color jitter, resized crops), optimizing management of a 6,000-image dataset and improving model generalization.}
        \resumeItem{Launched an AI-powered diagnostic dashboard integrating LLM-driven predictive models; collaborated with clinicians to deliver real-time patient risk assessments.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{HR Attrition Prediction System} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{}
        \resumeItemListStart
          \resumeItem{Conducted ML analysis on IBM's HR dataset—identified 16.12\% attrition rate and applied models like Logistic Regression and Random Forest, achieving up to 87.75\% accuracy.}
          \resumeItem{Extracted key attrition drivers (Monthly Income, Age, Over Time, Years Since Last Promotion, Job Satisfaction) and developed targeted strategies to reduce churn.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{National Rail Performance Insights Dashboard} $|$ \emph{Python, SQL, Tableau, Excel}}{}
        \resumeItemListStart
          \resumeItem{Engineered and supervised on-time performance and refund analyses—uncovered 81\% on-time contribution (£570K), diagnosed primary disruption causes (signal failures, staffing, weather), and formulated a revised refund policy to streamline customer compensation and enhance service reliability.}
          \resumeItem{Published plugin online; reached 2,000+ downloads and maintained a 4.5/5 average rating.}
          \resumeItem{Collaborated with server administrators for feedback and iterative improvements.}
        \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{Power Exchange Simulation} $|$ \emph{Python, SimPy, NumPy, Matplotlib}}{}
        \resumeItemListStart
          \resumeItem{Developed a discrete-event simulation model for electricity trading market dynamics, modeling buyer-seller interactions and price discovery mechanisms.}
          \resumeItem{Created comprehensive visualization dashboards displaying price trends, trading volumes, and market efficiency metrics for stakeholder analysis.}
          \resumeItem{Optimized simulation performance to handle 10,000+ trading events per day with real-time monitoring capabilities.}
        \resumeItemListEnd    
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: Python, R, SQL} \\
     \textbf{Data Science \& ML}{: Pandas, NumPy, Scikit-learn, Matplotlib, Seaborn, spaCy, Beautiful Soup, NLP} \\
     \textbf{Web Development}{: Django, Flask} \\
     \textbf{Databases \& Cloud}{:  MySQL, MongoDB, Google Cloud Platform} \\
     \textbf{Tools \& Platforms}{: Power BI, Tableau, Jupyter Notebook, Google Colab, VS Code, Cursor AI, Git, GitHub} \\
    }}
 \end{itemize}

%-----------SOFT SKILLS-----------
\section{Soft Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Flexible $|$ Collaborative $|$ Efficient Scheduler $|$ Task Coordination \\
    }}
 \end{itemize}


%------------------CERTIFICATIONS-------------------------
\section{Achievements}
\resumeItemListStart
    \resumeItem{SensAI @ CIT × HyperVerge Hackathon - Top 10 Finalist (2025): Led the development of a multilingual real-time AI feedback system with native-script and phonetic-transliteration support.}
    \resumeItem{redBus Data Decode Hackathon - Top 31 of 690 participants (2025): Forecasted demand for buses 15 days in advance by engineering Python-based models with AutoGluon.}
\resumeItemListEnd

\end{document}
